Bayesian Rate Estimation

### 2012-03-31 many.tex
Fixed minor typo in III A.

In Figure \ref{fig:analytic-rate-recovery}, we show the marginalized
posterior densities for the foreground and background rates recovered
from a synthetic data set drawn from the distributions in
Eqs.~\eqref{eq:analytic-background-rate} and
\eqref{eq:analytic-foreground-rate} with .  (Refer to
Eq.~\eqref{eq:rates-marginalized}.)  Figure
\ref{fig:analytic-rate-foreground-probs} shows the posterior
foreground probability for each event marginalized over all other
events' types and the foreground and background rates.  (Refer to
Eq.~\eqref{eq:foreground-marginalized}.)

>>>>

In Figure \ref{fig:analytic-rate-recovery}, we show the marginalized
posterior densities for the foreground and background rates.  (Refer
to Eq.~\eqref{eq:rates-marginalized}.)  Figure
\ref{fig:analytic-rate-foreground-probs} shows the posterior
foreground probability for each event marginalized over all other
events' types and the foreground and background rates.  (Refer to
Eq.~\eqref{eq:foreground-marginalized}.)
